---
title: "Protestantism Code"
author: "Duarte Amaro"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}

library(AER)
library(tidyverse)
library(sf)
library(marginaleffects)
library(SpatialRDD)
library(tmap)
library(rdrobust)
library(rddensity)
library(stringi)
library(readxl)
library(modelsummary)
library(purrr)
library(broom)

theme_set(theme_bw())

knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE,
                      fig.width = 10, fig.height = 7
                      #out.width = "14cm", out.height = "9.1cm"
                      )

```

# Cleaning the hand-transcribed data

```{r}


d_prots <- read_xlsx("Protestants by Commune - 1839.xlsx") |>
  rename(
    code_insee = `Code INSEE`,
    code_insee_full = `Code INSEE (Department, Arrondissement, Canton, Commune)`,
    pop_general = `Population générale`,
    pop_protestant = `Population Protestante`,
    pop_protestant_section = `Population protestante par section`,
    dist = `Distance du chef-lieu de chaque commune au chef-lieu de la section`,
    residence = `Résidence du pasteur`,
    obs = `...16`
  )


d_issues <- d_prots |> 
  filter(
    (code_insee %in% unique(d_prots$code_insee[duplicated(d_prots$code_insee) == TRUE])) | !is.na(obs)) |>
  dplyr::select(Departement, Communes, code_insee, pop_general, pop_protestant, obs)

nrow(d_issues)

#View(d_issues |> filter(is.na(code_insee)))

```

There are 116 rows which might be problematic, including repeated codes or observations left during coding.

Most rows lacking an INSEE code correspond to observations without reference to a concrete commune. Some mention a specific locality within a commune (e.g., Maine-Geoffroy in Royan or Saint-Césaire in Nîmes). These can be safely discarded.

One case relates to two observations for the commune of Les Salles-du-Gardon. One of them describes the left shore of the Gardon and corresponds geographically to the commune of La Grand-Combe, formed in 1846. The other describes the right shore of the Gardon, corresponding to the current commune of Les Salles-du-Gardon. The population mentioned for the first is the historical record for the entire pre-1846 commune. We have population estimates for both communes from 1846, when La Grand-Combe had 4 011 people and Les Salles-du-Gardon had 1 041. If the proportion had been the same in 1839, then out of the entire 1 224 people, about 972 would have lived in La Grand-Combe and 252 in Les Salles-du-Gardon. I will therefore assign the first observation to the modern-day commune of La Grand-Combe and the second to the modern-day commune of Les Salles-du-Gardon, with the population in each of them adjusted accordingly. These two communes should be removed from the analysis as a robustness check.

```{r}

d_salles <- d_issues |>
  filter(Communes %in% c("La Fovède, ou la partie de la commune des Salles, rive droite du Gardon", "La Grand Combe, ou la partie de la commune des Salles, rive gauche du Gardon")) |>
  mutate(
    code_insee = case_when(
      Communes == "La Fovède, ou la partie de la commune des Salles, rive droite du Gardon" ~ "30307",
      Communes == "La Grand Combe, ou la partie de la commune des Salles, rive gauche du Gardon" ~ "30132"
    ),
    pop_general = case_when(
      Communes == "La Fovède, ou la partie de la commune des Salles, rive droite du Gardon" ~ 252,
      Communes == "La Grand Combe, ou la partie de la commune des Salles, rive gauche du Gardon" ~ 972
    ),
    Communes = case_when(
      Communes == "La Fovède, ou la partie de la commune des Salles, rive droite du Gardon" ~ "Les Salles-du-Gardon",
      Communes == "La Grand Combe, ou la partie de la commune des Salles, rive gauche du Gardon" ~ "La Grand-Combe"
    )
  )

```


The other observations without a corresponding INSEE code are observations where no particular commune is mentioned; instead, the authors simply state 'neighbouring communes' or give a number of communes without specifying which these relate. We can estimate which communes these relate to by manually looking at a map and assuming that they are the neighbouring communes, and then simply divide the number of protestants among them (either equally or according to the population of each commune). Another option is to exclude any communes not explicitly mentioned from the analysis. A final option is to simply assign communes not explicitly mentioned a value of 0, which would bias the results towards finding no effect. For now, I will simply exclude these from the analysis.

We can now move to cases where there is an INSEE code but the commune is either duplicated or no longer exists.

We have 20 mergers: Saint-Maurice (17300), which merged with the the commune of La Rochelle (same code); Agonnay (17397) which merged with Saint-Savinien (same code); Rouquette, Saint-Sulpice-d'Eymet, and Cogulot (24167) which all merged with Eymet (same code); Le Canet and La Rouquette (24335) which merged with Port-Sainte-Foy-et-Ponchapt (same code); Puyguulhem and Mombos (24549) which merged with Thénac (same code); La Répara (26020) which merged with La Répara-Auriples; L'Escoulin (26128) which merged with Eygluy-Escoulin; La Bâtie-Crémazin (26136) which merged with Val-Maravel; Béconne (26276) merged with Roche-Saint-Secret-Béconne; La Ville-l'Évêque (28036) merged with Berchères-sur-Vesgre; Mainterne and Vitray-sous-Brézolles (28120) merged with Crucey-Villages; Bourneville (28190) merged with Guillonville; Cambo (30058) merged with La Cadière-et-Cambo; Saint-Martin-de-Sossenac (30106) merged with Durfort-et-Saint-Martin-de-Sossenac; Cézas (30325) merged with Sumène; Paroisse-du-Vigan (30350) merged with Le Vigan; Appelles (33369) merged with Saint-André-et-Appelles; Saint-Nazaire (33378) merged with Saint-Avit-Saint-Nazaire; Le Pouzat (7204) merged with Saint-Agrève; and Naves (7334) merged with Les Vans.

```{r}

d_merged <- d_issues |>
  filter(code_insee %in% c("17300", "17397", "24167", "24335", "24549", "26020", "26128", "26136", "26276", "28036", "28120", "28190", "30058", "30106", "30325", "30350", "33369", "33378", "7204", "7334")) |>
  mutate(pop_general = as.numeric(pop_general),
         pop_protestant = as.numeric(pop_protestant)) |>
  group_by(code_insee) |>
  summarise(
    Departement = first(Departement),
    Communes = first(Communes),
    pop_general = sum(pop_general),
    pop_protestant = sum(pop_protestant, na.rm = TRUE),
    obs = NA
  ) |>
  mutate(
    Communes = case_when(#code_insee %in% c("17300", "17397", "24167", "24335", "24549", "26020", "26128", "26136", "26276", "28036", "28190", "30106", "30350", "33369", "33378", "7204", "7334") ~ first(Communes),
                         code_insee == "28120" ~ "Crucey-Villages",
                         code_insee == "30058" ~ "La Cadière-et-Cambo",
                         code_insee == "30325" ~ "Sumène",
                         .default = Communes
                         )
  )

```


We then have cases where the same commune is mentioned twice. The true protestant population is therefore either the sum of each entry or one of the listed values.

For cases where it is only one the values, I have followed the conservative approach of using the lesser one. We have the case of Arvert (17021), mentioned twice with the same general population but different values of Protestants (658 and 727). As the sum is greater than the overall population, these are presumably two different measures of the same population. I will go with the conservative approach and use the lower value. Rémuzat (26264) is also listed twice although the protestant population could not retrieved from the first entry; I'll assume the second entry corresponds to the true value. Pommiers (30199) is a similar case, listed twice with the same general population but with different values for the protestant population. I will assume the lower value is correct. 

```{r}

d_duplicates_1 <- d_issues |>
  filter(code_insee %in% c("17021", "26264", "30199")) |> 
  mutate(pop_general = as.numeric(pop_general),
         pop_protestant = as.numeric(pop_protestant)) |>
  group_by(code_insee) |>
  summarise(
    Departement = first(Departement),
    Communes = first(Communes),
    pop_general = max(pop_general),
    pop_protestant = min(pop_protestant, na.rm = TRUE),
    obs = NA
  )
```


In the case of Marennes (17219), the same commune is listed twice and in immediate succession. One of the entries has a population a little above the registered overall population, at 4900 inhabitants, while the other is quite below at around 490. It would hardly be the case that the overall population corresponds to their sum; instead, the second entry probably refers to another commune and was mistakenly inputted as Marennes. I will therefore assume both population values are correct in the first entry. Chabeuil (26064) is also listed twice, once as 'Portion de Chabeuil'. It's made clear that the second entry corresponds to the whole Protestant population. Two entries were identified as referring to Saint-Germain-du-Seudre (17342), although one was only listed as Saint-Germain. It is possible that it refers to another commune, so I will assume that the second entry is the only correct one. Montdardier (30176) is listed twice, once with a slightly greater general population and another time with a value in line with the Cassini figures. The number of Prostestants differs - I will assume again the more conservative figure is correct. Péronville (28296) appears to be listed twice: once with a seemingly incorrect overall population and a protestant population of 20, and another time with a population more in line with the Cassini estimates but without listing the protestant population. I will assume the population was 20 but flagging this for the future. Similarly, Pranles (7184) is listed twice, once with a correct general population and another time with a much smaller general population. I will assume the second entry, with the correct population, is the more trustworthy value for the Protestant population as well.

```{r}


d_marennes <- d_issues |> 
  filter(code_insee == "17219" & pop_general == "4942")

d_chabeuil <- d_issues |> 
  filter(code_insee == "26064" & pop_general == "4295")

d_saint_germain <- d_issues |> 
  filter(code_insee == "17342" & pop_general == "812")

d_montdardier <- d_issues |> 
  filter(code_insee == "30176" & pop_general == "715")

d_peronville <- d_issues |> 
  filter(code_insee == "28296" & pop_general == "586") |>
  mutate(pop_protestant = "20")

d_pranles <- d_issues |>
  filter(code_insee == "7184" & pop_general == "1775")

d_duplicates_2 <- bind_rows(
  d_marennes,
  d_chabeuil,
  d_saint_germain,
  d_montdardier,
  d_peronville,
  d_pranles
)


```



Cases where the number of Protestants corresponds to the sum of each entry are more straighforward. Bois (17050) is similarly mentioned twice and with the same population. In this case, however, the values for the Protestant population are very small (10 and 13). It is possible that the real Protestant population here corresponds to their sum and I will therefore consider it as such. The case of Gageac-et-Rouillac (24193) is similar: the overall population listed is the same, the number of protestants differs and is quite small by reference to the overall population (50 and 70). Gardonne (24194) is listed twice, once as Partie Nord and another as Partie Sud. The overall population is the same but the protestant population differs, indicating that the total corresponds to their sum (140 and 47). Dourbies (30105) is also listed twice with the same general population but differing in their protestant population (30 and 40), which corresponds, I will assume, to their sum. Saint-André-de-Majencoules (30229) is listed twice, once as Hameau du Roy dans la commune de Saint-André-de-Majencoules, which suggests that the protestant population in the overall commune corresponds to their sum.

Finally, Les Ollières-sur-Eyrieux (7167) is listed twice with the total number of protestants corresponding to the sum, but with different population values. The overall population seems, on the basis of the Cassini figures, to correspond roughly to their sum as well.


```{r}


d_duplicates_3 <- d_issues |>
  filter(code_insee %in% c("17050", "24193", "24194", 
                           "30105", "30229")) |> 
  mutate(pop_general = as.numeric(pop_general),
         pop_protestant = as.numeric(pop_protestant)) |>
  group_by(code_insee) |>
  summarise(
    Departement = first(Departement),
    Communes = first(Communes),
    pop_general = first(pop_general),
    pop_protestant = sum(pop_protestant, na.rm = TRUE),
    obs = NA
  ) |>
  bind_rows(
    d_issues |>
      filter(code_insee == "7167") |> 
      mutate(pop_general = as.numeric(pop_general),
             pop_protestant = as.numeric(pop_protestant)) |>
      group_by(code_insee) |>
      summarise(
        Departement = first(Departement),
        Communes = first(Communes),
        pop_general = sum(pop_general, na.rm = TRUE),
        pop_protestant = sum(pop_protestant, na.rm = TRUE),
        obs = NA
      )
  )

d_solved <- bind_rows(
  d_salles |>
    mutate(pop_general = as.numeric(pop_general),
             pop_protestant = as.numeric(pop_protestant)),
  d_merged,
  d_duplicates_1,
  d_duplicates_2 |>
    mutate(pop_general = as.numeric(pop_general),
             pop_protestant = as.numeric(pop_protestant)),
  d_duplicates_3
)

```


We also have 66 entries where the population or the number of Protestants could not be established, many of which because there is no concrete commune to which the entry refers. There is also one observation where the Protestant population is greater than the overall population, Collorgues (30086). This value has been checked again against the digitised records and the mistake is not in the transcription. The observation has been discarded.

There are 1040 clean observations.


```{r}

d_clean <- d_prots |>
  filter(!(code_insee %in% unique(d_issues$code_insee))) |>
  dplyr::select(Departement, Communes, code_insee, pop_general, pop_protestant, obs) |>
  mutate(pop_general = as.numeric(pop_general),
         pop_protestant = as.numeric(pop_protestant)) |>
  bind_rows(d_solved) |>
  filter(!is.na(pop_general) & !is.na(pop_protestant) & pop_protestant <= pop_general) |>
  mutate(
    share_protestant = 100 * pop_protestant / pop_general
  )

```

While for some departments some observations state a rough number of communes, making it impossible to infer the number of protestants in the communes not explicitly mentioned, in others this is not the case and we could, in theory, assume that there are no Protestants in any communes not explicitly mentioned

```{r}

d_missing <- d_prots |> 
  mutate(pop_general_num = as.numeric(pop_general),
         pop_protestant_num = as.numeric(pop_protestant)) |>
  filter(is.na(pop_general_num) | is.na(pop_protestant_num))

names <- unique(d_clean$Departement[!(d_clean$Departement %in% unique(d_missing$Departement))])

```

# Adding Geospatial Data

```{r}
comm <- read_sf("commune-frmetdrom/COMMUNE_FRMETDROM.shp") |>
  filter(!(INSEE_DEP %in% c("971", "972", "973", "974", "976", "2A", "2B"))) |>
  rename(code_insee = INSEE_COM)
```

Each of the three following maps and corresponding dataframes follows one approach: 1) simply assign a value for the share of Protestants in 1839 to the communes explicitly mentioned in the original document, leaving all others NA; 2) as before, but also assigning a value of 0 to communes in departments mentioned in the original document and where no ambiguous "surrounding communes" are mentioned (e.g., Ariège (09), for which we have information on the concrete protestant population of some communes but no reference to any more dispersed population); 3) as before, but further assigning asigning a value of 0 to all communes in departments which should have been covered in the original document (i.e., any departments alphabetically prior to Hérault) but which are not mentioned. 

```{r}


d_map_1 <- full_join(d_clean |> 
            mutate(code_insee = as.numeric(code_insee)), 
          comm |>
            mutate(code_insee = as.numeric(code_insee)), by = "code_insee")

d_map_2 <- full_join(d_clean |> 
            mutate(code_insee = as.numeric(code_insee)), 
          comm |>
            mutate(code_insee = as.numeric(code_insee)), by = "code_insee") |>
  mutate(
    share_protestant = case_when(
      !is.na(share_protestant) ~ share_protestant,
      is.na(share_protestant) & INSEE_DEP %in% c("09", "12", "16", "24", "29", "31", "32", "34") ~ 0,
      .default = NA
    )
  )
  

deps <- unique(
  d_map_2$INSEE_DEP[!(
    d_map_2$INSEE_DEP %in% unique(d_map_2$INSEE_DEP[!is.na(d_map_2$share_protestant)])) & 
      as.numeric(d_map_2$INSEE_DEP) < 34]
  )

d_map_3 <- full_join(d_clean |> 
            mutate(code_insee = as.numeric(code_insee)), 
          comm |>
            mutate(code_insee = as.numeric(code_insee)), by = "code_insee") |>
  mutate(
    share_protestant = case_when(
      !is.na(share_protestant) ~ share_protestant,
      is.na(share_protestant) & 
        INSEE_DEP %in% c("09", "12", "16", "24", "29", "31", "32", "34") ~ 0,
      is.na(share_protestant) &
        INSEE_DEP %in% deps ~ 0,
      .default = NA
    )
  )
  

cowplot::plot_grid(d_map_1 |>
                     ggplot() +
                     geom_sf(aes(geometry = geometry,
                                 fill = share_protestant), colour = NA) +
                     scale_fill_gradient(low = "gold", high = "green4",
                                         na.value = "lightgrey") +
                     labs(title = "Share of Protestants in 1839 (Communes explicitly mentioned)"),
                   d_map_1 |>
                     ggplot() +
                     geom_histogram(aes(x = share_protestant), bins = 50),
                   ncol = 1)

cowplot::plot_grid(d_map_2 |>
                     ggplot() +
                     geom_sf(aes(geometry = geometry,
                                 fill = share_protestant), colour = NA) +
                     scale_fill_gradient(low = "gold", high = "green4",
                                         na.value = "lightgrey") +
                     labs(title = "Share of Protestants in 1839 (Departments mentioned with some zeros inputted)"),
                   d_map_2 |>
                     ggplot() +
                     geom_histogram(aes(x = share_protestant), bins = 50),
                   ncol = 1)

cowplot::plot_grid(d_map_3 |>
                     ggplot() +
                     geom_sf(aes(geometry = geometry,
                                 fill = share_protestant), colour = NA) +
                     scale_fill_gradient(low = "gold", high = "green4",
                                         na.value = "lightgrey") +
                     labs(title = "Share of Protestants in 1839 (All Departments up to Hérault with some zeros inputted)"),
                   d_map_3 |>
                     ggplot() +
                     geom_histogram(aes(x = share_protestant), bins = 50),
                   ncol = 1)

```

# Adding Electoral Data

```{r}
d2022 <- read_csv("cage_piketty/leg2022comm.csv")

d2017 <- read_csv("cage_piketty/leg2017comm.csv")

d2012 <- read_csv("cage_piketty/leg2012comm.csv")

d2007 <- read_csv("cage_piketty/leg2007comm.csv")

d2002 <- read_csv("cage_piketty/leg2002comm.csv")

d1997 <- read_csv("cage_piketty/leg1997comm.csv")

d1993 <- read_csv("cage_piketty/leg1993comm.csv")


d_FN <- bind_rows(
  d2022 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixRN) |>
    mutate(year = 2022),
  d2017 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2017),
  d2012 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2012),
  d2007 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2007),
  d2002 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2002),
  d1997 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 1997),
  d1993 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 1993)
) |>
  mutate(pvoixRN = case_when(
    year == 2022 ~ 100*pvoixRN,
    .default = 100*pvoixFN
  )) |>
  mutate(code_insee = as.numeric(codecommune)) |>
  right_join(d_map_1 |> filter(!is.na(share_protestant)))

d_FN_2 <- bind_rows(
  d2022 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixRN) |>
    mutate(year = 2022),
  d2017 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2017),
  d2012 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2012),
  d2007 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2007),
  d2002 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2002),
  d1997 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 1997),
  d1993 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 1993)
) |>
  mutate(pvoixRN = case_when(
    year == 2022 ~ 100*pvoixRN,
    .default = 100*pvoixFN
  )) |>
  mutate(code_insee = as.numeric(codecommune)) |>
  right_join(d_map_2 |> filter(!is.na(share_protestant)))

d_FN_3 <- bind_rows(
  d2022 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixRN) |>
    mutate(year = 2022),
  d2017 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2017),
  d2012 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2012),
  d2007 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2007),
  d2002 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 2002),
  d1997 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 1997),
  d1993 |> 
    dplyr::select(dep, nomdep, codecommune, nomcommune, pvoixFN) |>
    mutate(year = 1993)
) |>
  mutate(pvoixRN = case_when(
    year == 2022 ~ 100*pvoixRN,
    .default = 100*pvoixFN
  )) |>
  mutate(code_insee = as.numeric(codecommune)) |>
  right_join(d_map_3 |> filter(!is.na(share_protestant)))

```

Below is a simple regression of RN/FN voteshare since 1993 and the share of Protestants. For each method of dealing with NAs (see discussion above), I estimate a model with year FEs and another with year and department FEs.

```{r}

m1 <- lm(data = d_FN |> mutate(year = as.character(year)), pvoixRN ~ share_protestant + year)

m2 <- lm(data = d_FN|> mutate(year = as.character(year)), pvoixRN ~ share_protestant + year + dep)

m3 <- lm(data = d_FN_2 |> mutate(year = as.character(year)), pvoixRN ~ share_protestant + year)

m4 <- lm(data = d_FN_2 |> mutate(year = as.character(year)), pvoixRN ~ share_protestant + year + dep)

m5 <- lm(data = d_FN_3 |> mutate(year = as.character(year)), pvoixRN ~ share_protestant + year)

m6 <- lm(data = d_FN_3 |> mutate(year = as.character(year)), pvoixRN ~ share_protestant + year + dep)

modelsummary(list(m1, m2, m3, m4, m5, m6
                  ), 
             vcov = "robust", 
             stars = TRUE,
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "No", "Yes", "No", "Yes"
             ),
             #output = "table1.tex",
             #output = "text"
             )

```

# Adding Controls

We can now add some controls, including measures of religiosity (as measured by the share of constitutional priests in 1791, mean revenue, the share of the population with a baccalauréat or higher, and the share of the population with higher education). I am also including historic measures of human capital such as the literacy rate in 1816.

```{r}

religiosite1791 <- read_csv("cage_piketty/religiositecommunes1791.csv") |>
  dplyr::select(dep, nomdep, codecommune, nomcommune, pserment1791)

alphabetisation <- read_csv("cage_piketty/alphabetisationcommunes.csv") |> 
  dplyr::select(dep, nomdep, codecommune, nomcommune, 
                starts_with(c("pc")) & 
                  ends_with(c("1686", "1816", "1854")))

revenus0 <- read_csv("cage_piketty/revcommunes.csv") |>
  dplyr::select(dep, nomdep, codecommune, nomcommune, 
                ends_with(c("1839", "1993", "1997", 
                            "2002", "2007", "2012", "2017", "2022")))

revenus <- revenus0 |>
  dplyr::select(dep, nomdep, codecommune, nomcommune, 
                starts_with(c("revmoy1", "revmoy2"))) |>
  pivot_longer(cols = starts_with("rev"),
               names_to = "Year",
               values_to = "revmoy") |>
  mutate(Year = str_sub(Year, -4, -1)) |>
  full_join(revenus0 |>
  dplyr::select(dep, nomdep, codecommune, nomcommune, 
                starts_with(c("pop"))) |>
  pivot_longer(cols = starts_with("pop"),
               names_to = "Year",
               values_to = "pop") |>
  mutate(Year = str_sub(Year, -4, -1)))

diplomes <- read_csv("cage_piketty/diplomescommunes.csv") |>
   dplyr::select(dep, nomdep, codecommune, nomcommune, 
                 starts_with(c("pb", "ps")) & 
                   ends_with(c("1993", "1997", "2002", 
                               "2007", "2012", "2017", "2022"))) |>
  mutate(
    nomcommune = case_when(codecommune == "35363" ~ "PONT-PEAN",
                           .default = nomcommune)
  ) |>
  filter(codecommune != "91692") ## The name of the commune is listed as Butry-sur-Oise (which is in the wrong department and has a different code)

diplomes <- diplomes |> 
  pivot_longer(cols = starts_with("pbac"), 
               names_to = "Year", 
               values_to = "pbac") |>
  mutate(Year = str_sub(Year, -4, -1)) |> 
  full_join(diplomes |> 
              pivot_longer(cols = starts_with("psup"), 
                           names_to = "Year", values_to = "psup") |> 
              mutate(Year = str_sub(Year, -4, -1))) |> 
  dplyr::select(-ends_with(c("1993", "1997", "2002", 
                             "2007", "2012", "2017", "2022"))) 

d_controls <- full_join(diplomes, 
                        revenus |>
                          rename(nomcommune_2 = nomcommune), 
                        by = c("dep", "nomdep", "codecommune", "Year")) |>
  full_join(religiosite1791 |>
              rename(nomcommune_3 = nomcommune,
                     nomdep_3 = nomdep),
            by = c("dep", "codecommune")
            ) |>
  full_join(alphabetisation|>
              rename(nomcommune_4 = nomcommune),
            by = c("dep", "nomdep", "codecommune")
            ) |>
  dplyr::select(-c(nomcommune_2, nomcommune_3, nomdep_3, nomcommune_4))

nrow(d_controls) == 7*(c(revenus$codecommune, diplomes$codecommune, religiosite1791$codecommune, alphabetisation$codecommune) |> unique() |> length())

```


```{r}

d_FN_controls <- left_join(d_FN |>
                             mutate(Year = as.character(year)), 
                           d_controls, by = c("dep", "nomdep", "codecommune", 
                                              "nomcommune", "Year"))

d_FN_controls_2 <- left_join(d_FN_2 |>
                               mutate(Year = as.character(year)), 
                             d_controls, by = c("dep", "nomdep", "codecommune", 
                                                "nomcommune", "Year"))

d_FN_controls_3 <- left_join(d_FN_3 |>
                               mutate(Year = as.character(year)), 
                             d_controls, by = c("dep", "nomdep", "codecommune", 
                                                "nomcommune", "Year"))

```

The following models consider only the communes explicitly mentioned in the original document.

```{r}
m1 <- lm(data = d_FN_controls |> 
           mutate(year = as.character(year)), 
         pvoixRN ~ share_protestant + year)

m2 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep)

m3 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop)

m4 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup)

m5 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac)

m6 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac + pconjsign1816)

m7 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac + pconjsign1816 + pserment1791)


modelsummary(list(m1, m2, m3, m4, m5, m6, m7
                  ), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pconjsign1816" = "Literacy in 1816",
               "pserment1791" = "Share of constitutional priests in 1791"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"
             ),
             #output = "table1.tex",
             #output = "text"
             )

```


```{r, fig.width=10}

results <- d_FN_controls |>
  group_by(Year) |>
  group_modify(~ {
    model <- lm(
      pvoixRN ~ share_protestant + dep + revmoy + pop + psup + pbac + 
        pconjsign1816 + pserment1791,
      data = .x
    )
    
    tidy(model, conf.int = TRUE) |>
      filter(term == "share_protestant")
  }) |>
  ungroup() |>
  mutate(
    group = "1"
  ) |>
  bind_rows(
    d_FN_controls_2 |>
      group_by(Year) |>
      group_modify(~ {
        model <- lm(
          pvoixRN ~ share_protestant + dep + revmoy + pop + psup + pbac + 
            pconjsign1816 + pserment1791,
          data = .x
        )
        
        tidy(model, conf.int = TRUE) |>
          filter(term == "share_protestant")
      }) |>
      ungroup() |>
      mutate(
        group = "2"
      )
  ) |>
  bind_rows(
    d_FN_controls_3 |>
      group_by(Year) |>
      group_modify(~ {
        model <- lm(
          pvoixRN ~ share_protestant + dep + revmoy + pop + psup + pbac + 
            pconjsign1816 + pserment1791,
          data = .x
        )
        
        tidy(model, conf.int = TRUE) |>
          filter(term == "share_protestant")
      }) |>
      ungroup() |>
      mutate(
        group = "3"
      )
  )

ggplot(results, aes(x = as.numeric(Year), y = estimate, colour = group)) +
  geom_point(position = position_dodge(2)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                width = 0.2,
                position = position_dodge(2)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_colour_manual(values = c("1" = "blue", "2" = "orange", "3" = "green4"),
                      labels = c("1" = "Only Communes Explicitly Mentioned",
                                 "2" = "All Departments Mentioned (Zeros Inputted)",
                                 "3" = "All Departments up to Hérault (Zeros Inputted)"),
                      name = "") +
  labs(
    x = "Year",
    y = "Coefficient of Share of Protestants",
    title = "Coefficient of Share of Protestants by Year",
    subtitle = "Controlling for Department FEs, Average Income, Population, Share of Bac, Share of Higher Education,\nLiteracy in 1816, and Share of Constitutional Priests in 1791"
  ) +
  theme(legend.position = "bottom")

```


```{r}
m1 <- lm(data = d_FN_controls |> 
           mutate(year = as.character(year)), 
         pvoixRN ~ log(share_protestant + 1) + year)

m2 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep)

m3 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop)

m4 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup)

m5 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac)

m6 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac + pconjsign1816)

m7 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac + pconjsign1816 + pserment1791)


modelsummary(list(m1, m2, m3, m4, m5, m6, m7
                  ), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "log(share_protestant + 1)" = "Log of Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "pserment1791" = "Share of constitutional priests in 1791",
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pconjsign1816" = "Literacy in 1816"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"
             ),
             #output = "table1.tex",
             #output = "text"
             )

```

```{r}


m1 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         psup ~ share_protestant + year + dep + revmoy + pop)

m1log <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         psup ~ log(share_protestant + 1) + year + dep + revmoy + pop)

m2 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         psup ~ share_protestant + year + dep + revmoy + pop + pconjsign1816 + pserment1791)

m2log <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         psup ~ log(share_protestant + 1) + year + dep + revmoy + pop + pconjsign1816 + pserment1791)

m3 <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pconjsign1816 ~ share_protestant + year + dep + revmoy + pop)

m3log <- lm(data = d_FN_controls|> 
           mutate(year = as.character(year)),
         pconjsign1816 ~ log(share_protestant + 1) + year + dep + revmoy + pop + pserment1791)

modelsummary(dvnames(list(m1, m1log, m2, m2log, m3, m3log
                  )), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839",
               "log(share_protestant + 1)" = "Log of Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pserment1791" = "Share of constitutional priests in 1791",
               "pconjsign1816" = "Literacy in 1816"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m1log, ~m2, ~m2log, ~m3, ~m3log, 
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
             ),
             #output = "table1.tex",
             #output = "text"
             )


```

```{r}

m1 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)), 
         pvoixRN ~ share_protestant + year)

m2 <- lm(data = d_FN_controls_2|> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep)

m3 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop)

m4 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup)

m5 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac)

m6 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac + pconjsign1816)

m7 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac + pconjsign1816 + pserment1791)

m8 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         psup ~ share_protestant + year + dep + revmoy + pop)

m9 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         psup ~ share_protestant + year + dep + revmoy + pop + pconjsign1816)

m10 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pconjsign1816 ~ share_protestant + year + dep + revmoy + pop)

stargazer::stargazer(m1, m2, m3, m4, m5, m6, m7, m8, m9, type = "text", omit.stat = c("f", "ser"), star.cutoffs = c(0.05, 0.01, 0.001), omit = c("year", "dep"))

modelsummary(dvnames(list(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10
                  )), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pserment1791" = "Share of constitutional priests in 1791",
               "pconjsign1816" = "Literacy in 1816"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8, ~m9, ~m10,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
             ),
             #output = "table1.tex",
             #output = "text"
             )


```

```{r}

m1 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)), 
         pvoixRN ~ share_protestant + year)

m2 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep)

m3 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop)

m4 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup)

m5 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac)

m6 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac + pconjsign1816)

m7 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ share_protestant + year + dep + revmoy + pop + psup + pbac + pconjsign1816 + pserment1791)

m8 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         psup ~ share_protestant + year + dep + revmoy + pop)

m9 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         psup ~ share_protestant + year + dep + revmoy + pop + pconjsign1816)

m10 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pconjsign1816 ~ share_protestant + year + dep + revmoy + pop)

modelsummary(dvnames(list(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10
                  )), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pserment1791" = "Share of constitutional priests in 1791",
               "pconjsign1816" = "Literacy in 1816"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8, ~m9, ~m10,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
             ),
             #output = "table1.tex",
             #output = "text"
             )


```

```{r}

m1 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)), 
         pvoixRN ~ log(share_protestant + 1) + year)

m2 <- lm(data = d_FN_controls_2|> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep)

m3 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop)

m4 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup)

m5 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac)

m6 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac + pconjsign1816)

m7 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac + pconjsign1816 + pserment1791)

m8 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         psup ~ log(share_protestant + 1) + year + dep + revmoy + pop)

m9 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         psup ~ log(share_protestant + 1) + year + dep + revmoy + pop + pconjsign1816)

m10 <- lm(data = d_FN_controls_2 |> 
           mutate(year = as.character(year)),
         pconjsign1816 ~ log(share_protestant + 1) + year + dep + revmoy + pop)

stargazer::stargazer(m1, m2, m3, m4, m5, m6, m7, m8, m9, type = "text", omit.stat = c("f", "ser"), star.cutoffs = c(0.05, 0.01, 0.001), omit = c("year", "dep"))

modelsummary(dvnames(list(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10
                  )), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839",
               "log(share_protestant + 1)" = "Log of Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pserment1791" = "Share of constitutional priests in 1791",
               "pconjsign1816" = "Literacy in 1816"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8, ~m9, ~m10,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
             ),
             #output = "table1.tex",
             #output = "text"
             )


```

```{r}

m1 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)), 
         pvoixRN ~ log(share_protestant + 1) + year)

m2 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep)

m3 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop)

m4 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup)

m5 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac)

m6 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac + pconjsign1816)

m7 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pvoixRN ~ log(share_protestant + 1) + year + dep + revmoy + pop + psup + pbac + pconjsign1816 + pserment1791)

m8 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         psup ~ log(share_protestant + 1) + year + dep + revmoy + pop)

m9 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         psup ~ log(share_protestant + 1) + year + dep + revmoy + pop + pconjsign1816)

m10 <- lm(data = d_FN_controls_3 |> 
           mutate(year = as.character(year)),
         pconjsign1816 ~ log(share_protestant + 1) + year + dep + revmoy + pop)

modelsummary(dvnames(list(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10
                  )), 
             vcov = "robust", 
             stars = TRUE,
             
             coef_omit = "year|dep",
             coef_map = c(
               "(Intercept)" = "Constant",
               "share_protestant" = "Share of Protestants in 1839",
               "log(share_protestant + 1)" = "Log of Share of Protestants in 1839",
               "revmoy" = "Average income",
               "pop" = "Population", 
               "psup" = "Percentage of people with higher education",
               "pbac" = "Percentage of people with the bac",
               "pserment1791" = "Share of constitutional priests in 1791",
               "pconjsign1816" = "Literacy in 1816"),
             gof_map = tibble::tribble(~raw, ~clean, ~fmt,
                                       "nobs", "N", 0,
                                       "r.squared", "R^2", 2,
                                       "adj.r.squared", "Adj. R^2", 2),
             add_rows = tibble::tribble(
               ~term, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8, ~m9, ~m10,
               "Year FE", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Department FE", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
             ),
             #output = "table1.tex",
             #output = "text"
             )


```

